Title Goes Here

### 2024-05-24 analysis/paper/paper.qmd

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability")

@@

```{r}
ggplot(word_data, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  coord_flip() +  # Flips the axes for easier reading of text
  labs(x = "Words", y = "Frequency", title = "Word Frequency")
```

>>>>

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%

  count(word, sort = TRUE) %>%
  drop_na()

# here's the list of words of interest
community_word <- c("women","color","religion","race","age","veteran","disability","citizenship","ancestry","national origin","nondiscrimination","sex","gender","marital status","genetic information","breastfeeding","sexual orientation","discriminate","transgender status","gender expression","veteran")
count(word, sort = TRUE)

@@

```{r}
ggplot(EEO_clean, aes(x = reorder(word, n), y = n)) +
  geom_col() +
  labs(x = "Words", y = "Frequency", title = "Word Frequency") +
  ylim(10,50)
```
